---
title: "Interacting with APIs: Census Vingette"
author: "Autumn Locklear"
output:
  github_document:
    toc: true
    html_preview: false

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a vignette demonstrating how to interact with an API. I used the US Census API to show how I call the data. I wrote functions to interact with different endpoints.

# Requirements

I used the following packages to interact with the census API...
- [`censusapi`](https://www.rdocumentation.org/packages/censusapi/versions/0.8.0):a lightweight package to get data from the U.S. Census Bureau's APIs.
- [`tidycensus`]()
I used the following packages in the remainder of the document...
```{r echo=FALSE, warning = FALSE, message=FALSE}
#Download these packages...
library(censusapi)
```

```{r}
#Call some state-level data
state_pop <-getCensus(name = "2019/pep/charage",
  vars = c("AGE", "RACE","SEX", "GEO_ID"),
  region = "state:*",
  key = "0ea1c54391f6e63ed7165ae06c9d8524b7415e40")
head(pop_demo)
```

```{r}
#Call some county-level data
county_pop <- getCensus(name = "2019/pep/charage",
  vars = c("AGE", "RACE", "SEX"))
  region = "county"
```

